%\VignetteIndexEntry{genomationData}
%\VignetteKeywords{genomationData}
%\VignettePackage{genomationData}
%\VignetteEngine{knitr::knitr}

\documentclass[12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{geometry}


\newcommand{\Rcode}[1]{{\texttt{#1}}}
\newcommand{\Rpackage}[1]{{\textit{#1}}}

\author{Altuna Akalin, Vedran Franke}

\title{\textsf{genomationData: R package with high throughput genomic data}}
\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm,nomarginpar}



\date{October 25, 2013}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\begin{document}


\maketitle

\tableofcontents

% ----------------------------------------------------------------- %
\section{Introduction}

\Rpackage{genomationData} is a Bioconductor-compliant R package that contains 
raw and processed data from high throughput genomics experiments. The data is 
originaly intended for demo of the Bioconductor package \Rpackage{genomation}.
\Rpackage{genomationData} holds data from CHiP Seq and Bisulphite sequencing 
experiments produced by Encode and Epigenetics Roadmap. All datasets come from 
human H1 embryonic stem cell line and are mapped to the hg19/GRCh37 version of 
the genome.


% ----------------------------------------------------------------- %
\section{Getting started}

To load the \Rpackage{genomationData} package into your R envirnoment type:
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(genomationData)}
\end{alltt}
\end{kframe}
\end{knitrout}


\subsection{Sample description}
To list the available files type:
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{list.files}\hlstd{(}\hlkwd{system.file}\hlstd{(}\hlstr{"extdata"}\hlstd{,} \hlkwc{package} \hlstd{=} \hlstr{"genomationData"}\hlstd{))}
\end{alltt}
\end{kframe}
\end{knitrout}


The package currently holds 5 CHiP Sequencing and one Bisulfite sequencing 
samples. 
Files with the .bam extension contain raw CHiP seq reads, while *.broadPeak and 
*.narrowPeak represent processed peaks. 
Due to the large sizes of the samples, the *.bam files have been restricted to 
human chromosome 21 (chr21).

H1.Bisulfite-Seq.combined.chr21.bedGraph.gz' contains methylation calls for each
CpG dinucleotide on human chromosome 21. 
The original file was converted from wig into bedGraph format using the standard
UCSC applications.

To see complete information about the files, take a look into SamplesInfo.txt
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{samp.file} \hlkwb{=} \hlkwd{system.file}\hlstd{(}\hlstr{'extdata/SamplesInfo.txt'}\hlstd{,}
                        \hlkwc{package}\hlstd{=}\hlstr{'genomationData'}\hlstd{)}
\hlstd{samp.info} \hlkwb{=} \hlkwd{read.table}\hlstd{(samp.file,} \hlkwc{header}\hlstd{=}\hlnum{TRUE}\hlstd{,} \hlkwc{sep}\hlstd{=}\hlstr{'\textbackslash{}t'}\hlstd{)}
\hlkwd{head}\hlstd{(samp.info)}
\end{alltt}
\end{kframe}
\end{knitrout}


% ----------------------------------------------------------------- %
\section{Session Info}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{sessionInfo}\hlstd{()}
\end{alltt}
\begin{verbatim}
## R version 3.0.2 (2013-09-25)
## Platform: x86_64-w64-mingw32/x64 (64-bit)
## 
## locale:
## [1] LC_COLLATE=Croatian_Croatia.1250  LC_CTYPE=Croatian_Croatia.1250   
## [3] LC_MONETARY=Croatian_Croatia.1250 LC_NUMERIC=C                     
## [5] LC_TIME=Croatian_Croatia.1250    
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] knitr_1.5
## 
## loaded via a namespace (and not attached):
## [1] evaluate_0.5.1 formatR_0.10   highr_0.3      stringr_0.6.2 
## [5] tools_3.0.2
\end{verbatim}
\end{kframe}
\end{knitrout}


\bibliographystyle{apalike}
\bibliography{genomationData}
\end{document}
